On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 bqp.tex
Rewrite blind sampbqp section
Fix some labels and references

We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.

@@

\begin{thm}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

Finally, we prove \cref{thm:QPIP0BQP}.
We use Mahadev's measurement protocol from \cite{mahadev_delegation} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.

>>>>

We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{FOCS:Mahadev18a}, which is in turn taken from \cite{mf16}.

@@

\begin{thm}
	\label{thm:BlindBQP}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

Finally, we prove \cref{thm:QPIP0BQP}.
We use Mahadev's measurement protocol from \cite{FOCS:Mahadev18a} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.

### 2020-02-09 hamiltonian.tex
Fix some labels and references

The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
Protocols to delegate $\BQP$ computations such as \cite{mahadev_delegation} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
\Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}

>>>>

The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
\Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}

### 2020-02-09 preliminaries.tex
Restructure BQP protocols and rewrite proof
Fix some labels and references

\subsection{Quantum Prover Interactive Protocol (QPIP)}
We classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.

@@

>>>>

\subsection{Quantum Prover Interactive Protocol (QPIP)}
We classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{FOCS:Mahadev18a}.

@@

\def\QHE{\mathsf{QHE}}
\def\QGen{\mathsf{QHE.Keygen}}
\def\QEnc{\mathsf{QHE.Enc}}
\def\QEval{\mathsf{QHE.Eval}}
\def\QDec{\mathsf{QHE.Dec}}

### 2020-02-09 qpip0.tex
Updates from Overleaf
Fix some labels and references

\hannote{In this section, we modify the construction of \cite{mahadev_delegation} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.

Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

%Subprotocol for Quantum Measurements
\subsection{$\QPIP_0$ for BQP?}
\hannote{Ethan old description before parallel rep.}
As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

@@

In her groundbreaking work, Mahadev~\cite{mahadev_delegation} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.

@@

\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

        \item 
For any fixed $\gamma$ and $c\in [m]$ such that $c\neq i$\hannote{check}\hannote{for all k, y}, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   \hannote{$M_x?$}
\end{enumerate}
\end{lemma}

>>>>

\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.

Here we combine \autoref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

%Subprotocol for Quantum Measurements
\subsection{$\QPIP_0$ for BQP?}
\hannote{Ethan old description before parallel rep.}
As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

@@

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave the following 4-round interactive protocol to let a $\BQP$ machine "commit a $XZ$ measurement" to a classical machine.

@@

\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

        \item 
For any fixed $\gamma$ and $c\in [m]$ such that $c\neq i$\hannote{check}\hannote{for all k, y}, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{i}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   \hannote{$M_x?$}
\end{enumerate}
\end{lemma}
